A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-02 paper.tex
typo

\begin{abstract} 
%cite IoT data subscription economy
The Internet of Things (IoT) makes our lives simple and easier by automating mundane processes with devices around us. Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy, which devices can share and trade their resources. The real-time data exchangements among devices are periodically that only data in a specific time period is interested. Thus, publish/subscribe (pub/sub) communication model of streaming data with efficiency and flexibility corresponds such use case. Additionally, the economic layer built on top of subscription-based pricing models as Software-as-a-Service (SaaS) enables monetizing the subscription relationship, which the payment of data streams is calculated with data usage instead of a particular price for a fixed data set. This pricing model allows data providers to have a better vision of managing budgets and data consumers to have the flexibility to subscribe and unsubscribe. However, unlike static data sets, the streaming data increases the importance and difficulties of dynamic data ownership and identity verification. Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threaten the trust foundation of the entire system. Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants. Besides, consider handling the jobs and trading processes at the same time is too heavy for low-level IoT devices, an automated subscription procedures is also required. In this paper, we leverage usages of distributed ledger techonologies (DLTs) to construct a decentralized and trusted data trading platform on top of the IoT brokered infrastructure. This approach can efficiently enhance the degree of transparency and scalability. The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the trading process is automated through smart contracts. Finally, the prototype is implemented and evaluated.
\end{abstract}

\begin{IEEEkeywords}
Data Marketeplace, decentralization, Distributed Ledger Technology
\end{IEEEkeywords}

@@

% SaaS
The economic incentive model in our proposed IoT data trading platform works as subscription service that valuates the payments by data usage. The subscription-based models (e.g. SaaS and platform-as-a-service (PaaS)) are embedded in our lives, such as newspaper, video/audio streaming and softwares, which can bring enormous operating incomes and offer advantages that allows service providers have the flexibility in resource planning as well as a better prediction of revenue streams. And for service consumers, they can subscribe and unsubscirbe the services at will at anytime. The subscription-based model can easily adapts the underlying pub/sub communication model and benefit both data providers and consumers which promotes a good circulation of the platform. In \cite{SaaS}, the author pointed out that the strength of the relationships between consumers and providers of subscription-based services depends on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.

%trustless & automated
%trust: 對系統、對身份、對資料
In data trading platforms, there are three major aspects that need trust: identity, data ownership and trading. Proving the identity as well as the ownership of data is a challenging issue among various roles in a large scale platform. In current systems, trusted third-party authority like CA is widely adopted to certify each member. However, building trust upon CA is dangerous and fragile. The compromise of routers or CA can break the trust of entire system, and the data portability of using third-party services is still under suspicion. Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate General Data Protection Regulation (GDPR)\cite{GDPR}. Besides CA and storage, the subscrition history of data consumer may reveal his/hers interests and the exposure of personal information during trading process against GDPR as well. The final trust is trading procedures, apart from setting up the agreement between providers and consumers, both of them need to confirm that the agreement will be executed even if one party fails to comply.

@@

\subsection{Contributions}
The contributions in the paper are summarized as follow:
\begin{itemize}
	\item Standing on our proposed decentralized data trading infrastructure, we review several decentralized data trading architectures as well as the existing distributed storage, and clarify the necessity of using MAM.  
    \item We make an in-depth analysis of each layer of MAM, in addition to the performance evaluation and optimization of the current implementation. We also compare the perfomance of exchanging different cryptosystems.
	\item We analyze the security concerns when offloading MAM operations to brokers, and propose a solution to resolve them.
\end{itemize}

@@

%TODO: cite IOTAIdustryMarketplace
\section{Related Work}
\label{section:relatedWork}
% pub/sub
\subsection{Data exchange mechanism for IoT}
The publish/subscribe service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications. A lot of work in publish/subscribe system focused on the scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset. A few work targets on the storage which is a vital consideration for IoT and mobile computing and the incentive for data economics.

M. B. Abdullahi and G. Wang\cite{centralPubSub} presented a secure publish/subscribe data storage service in Wireless sensor networks (WSNs) which ensures several security issues. Each user has an identity for authentication, whereas subscribers' interests are encoded before matching to protect users' interests. Additionally, the proposed encryption scheme can prevent adversary to access published data if the sensor node is compromised. However, the access control and encryption keys of data is enforced by the network controllers (NCs) and CAs, which may be a potential security risk of the system. Also the storage is not well illustrated in the work. G. S. Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data. With the help of Ethereum smart contract, usesrs can perform data validation easily, and brokers can keep track of data status. But data is plaintext on blockchain, which the privacy problem of sensitive data need to be considered carefully. The economics incentives that can encourage the publishers to participate the system and pay more attention on the quality control are not included.

In \cite{userCentricData}, the publisher runs a node in blockchain that preserves all the history data of the ledger, therefore, they can publish and manage data without any third-parties. The subscribers request publisher directly and ask them to save a cache space for interested data. The main contribution of the system is to ensure data owners have full controls of produced data, but the data owners need to have well devices and environment to perform such functionalities and preserve data. Also, the rights for accessing digital assets is more compatible in the IoT scenarios instead of copying raw data. Secure Pub-Sub model\cite{SPS}, a brokerless of publish/subscribe model, is proposed to eliminate the security risk of middlewares in the model and to provide a reputation-based fairness payment strategy on blockcahin. The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent. The reputation system and the punishment rules against malicous acts of subscribers and publishers. Yet, without brokers, providers and subscribers may need to reveal more sensitive information like IP address in order to match the both sides. Another broker-less model in \cite{PrivacyPreservPubSub} protects the subscribers' privacy by encrypting users' interests with the light-weight PKEwET\cite{PKEwET}, which allows publishers to match the subscribers' interests in cipher text.

\subsection{Trusted IoT Trading Infrastructure}
Multiple infrastructures for trusted IoT data trading have been proposed by Paolo Missier et. al\cite{MindMyValue} presenting an IoT brokered infrastructure based marketplace which enables trading with Ethereum smart contracts. The brokers are only responsible for data transmission in order to adapt flexible agreement between participants. Unlike the standard pub/sub model that matches publishers and subscribers that participants are unaware of each other. However, the data cubes (i.e., a tuple of information, such as provider, subscriber and time period) are stored in a centralized Cassandra NoSQL database, which is guarateed to be tamperproof but the risk of single point failure still exists.

A. Colman et al. \cite{TrustedMarketplaceWearable} discussed on trading the sensitive data among wearables. Several security issues are well discussed and solved with DLTs in the paper, the system consists of multiple components that has its different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts. While the trading processes are splited into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.

In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamperproof and authentication functionalities by tailoring messages to a channel. Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system. Considering the limited transaction processing capability of DLT, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM for further exchangement. This research takes MAM as data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet. A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offered a key and entry points management with MAM that minimize the information which data producers need to hold. Also, Ethereum smart contract is used to maintain an authorized user list and to enable trading. However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading and iteractions between providers and consumers are not illustrated in this paper.

@@

O. Lamtzidis and J. Gialelis \cite{IOTASensorNode} proposed a distributed sensor node system to exchange data and establish a data monetization economy paradigm. The Back-End server helps sensor nodes to accelerate data uploads to MAM, manages keys and metadatas of data streams, and evaluates data price according to its quality. Furthermore, the Back-End server operates an user friendly interface of the marketplace and tackles all trading procedures. The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players. And the pricing strategy allows buyout, but does not take subscribe/unsubscribe based diagram into consideration. The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without the existence of any intermediate server but data providers only, data providers attach and trade data streams via MAM. With MAM, the data streams subscription is enabled, yet the conditions and details like refund and unsubscription are not discussed in this paper.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.5in]{pub_sub_model}
    \caption{The players in data subsciption-based trading platform consists of data providers, data consumers and brokers.}
    \label{fig:pub_sub_model}
\end{figure}

\begin{itemize}
\item \textbf{Data Provider: }
Data providers are the ones that generate streaming data and set the data price based on the different types of data. With the subscription fee that earned via trading, data providers are incentivized to maintain and improve the quality of data.
\item \textbf{Data Consumer: }
Data consumers are entities that are willing to buy data streams. As it is laborious to widely deploy devices to collect data from scratch, and without a marketplace, it is also difficult to find providers of the data sets, purchases is the fastet and efficient way to get the desired data sets.
\item \textbf{Broker: }
Brokers are responsible for building an agreement between data providers and consumers. Also brokers can represent data providers to perform computing tasks as brokers are expected to have higher resource.
\end{itemize}

@@

\subsection{Choice of Data Storage}
Data storage is the trust basis of data trading platforms where the data assets are reserved. Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots. Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well. In our proposed architecture, we adopt MAM as data storage to resolve the challenges of managing and verifying data streams. MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams. Carrying these properties, MAM is also appropriate for building a self-soverign identity system where the identity information such as public key, unique identifiers of services and metadatas are stored. One can easily prove himself by sharing the identifier on MAM without any authority.

@@

\begin{itemize}
    \item \textbf{Scalability}: For both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible
    \item \textbf{Integrity}: 
	\begin{itemize}    	
    	\item Messages published to the Tangle are tamperproof that against malicious modification.
    	\item Messages are signed with the keys pre-generated under Merkle signature scheme\cite{MSS} (MSS) that both keys and messages can be verified by participants.
    \end{itemize}
    \item \textbf{Confidentiality}:
    \begin{itemize}    	
    	\item The encrypted data are uploaded that only participants that have keys can decrypt.
    	\item The authorized users can retrieve data streams, since data is written on the Tangle which can be queried as long as the IOTA network is alive.
    	\item MAM provides forward-secrecy. The entry points of future data can be derived, but it's impossible to trace back those in the past. This feature prevents adversaries from retrieving published history even if the key is revealed.
    \end{itemize}
\end{itemize}

@@

% alternative solution => IPFS(data) + MAM(index)
\subsection{Digital Identity}
The digital identity represents an entity and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions. In our architecture, a self-soverign identity system TangleID\cite{TangleID} is used to manage the identity information that allow entities to prove its identity without any third-party authority. TangleID is built on top of MAM where change logs of the Decentralized Identifiers (DIDs)\cite{DID} defined by W3C is traceable. The identity information such as public key, unique identifiers of services and metadatas consist a DID document. One can easily prove himself by sharing the identifier on MAM without any authority.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{TangleID}
    \caption{To participate the data trading, players are required to have DID document issued by TangleID. The Consumer first need to send a registration request to TangleID to get the MAM channel ID of DID document and a public/private key pair for authentication. When the trade establish, the consumer sends the DID MAM channel ID to provider in order to perform encryption key exchangement. The data provider can then retrieve the consumer's public key and encrypt the content with it. After the consumer gets the encrypted message, he/she can decrypt the ciphertext with private key and finally get the encryption key of data product.}
    \label{fig:TangleID}
\end{figure}

@@

With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be acheived. In our system, \textbf{Product Contract} is made for the product launching and trading. The information of data products such as address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period and the broker-verified encryption key are listed on Product Contract. Listing. \ref{lst:constructor} list the data fields of Product Contract, and Fig.~\ref{fig:smart_contract_mam} shows the relationship of Product Contract and MAM. Furthermore, the participants can exchange encryption keys without any authorities via smart contracts. Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants.

@@

As for MAM operations, the performance results in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore we present an alternative solution for data providers to delegate these computing tasks to powerful proxy servers, Tangle-accelerator\cite{TA}, while ensuring the privacy. The details would be further illustrated in Section.\ref{section:ta_endpoint}.

\section{Masked Authenticate Messaging}
Data storage is the trust basis of data trading platforms where the data assets are reserved. Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots. Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well. In our proposed architecture, we adopt Masked Authenticated Messaging (MAM)\cite{MAM} as data storage to resolve the challenges of managing and verifying data streams. MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams. Carrying these properties, MAM is also appropriate for building a self-soverign identity system where the identity information such as public key, unique identifiers of services and metadatas are stored. One can easily prove himself by sharing the identifier on MAM without any authority.

@@

%classify
The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages. For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs. Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statitics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products. To do the classification in other distributed storage also encounters the aforementioned scalability problem, data entrypoints of the data steams should be reserved.

%data trace
Moreover, data tracability is an important security issue that allows users to track the changes of data. Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity. Yet the hash values of each new version are unrelated and it's hard to point out the differences between versions. MAM benefits from the singly linked-list data structure which attaches messages chronologically, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.

The operations of MAM are frequent, especially for data providers, who either upload data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace. In this paper, we evaluate the performance of MAM, and improve the effeciency with different strategies. Also, we take offloading the computation tasks to brokers as another possiblie approach for IoT devices, since brokers are considered to have higher computating power.

@@

\section{Decentralized Data Marketplace Case Study}
Trading Models of Decentralized Data Marketplace
\subsubsection{Set Up}
All participants need to register on TangleID\cite{TangleID}, a self-soverign identity system built on top of MAM, enables authentication without any third party via a decentralized identifiers and a public/private key pair for authentication.

@@

The details of data product, such as data price, MAM channel/endpoint ID and time period are listed on the Product Contract. As regard to the encryption key of data product, it is certified by a broker with blind signature\cite{blindSig}, a mechanism that allows users to sign contents without knowing it, and written the signed key on the Product Contract. This provides an approach for data consumers to verify the encryption key that avoid data providers frauding data consumers with a wrong one. The workflow is shown in Fig.~\ref{fig:launching_product}.

@@

\subsubsection{Trading}
Data consumers pay subscription fees to the Product Contract of desired data products, and data providers give the "access" of data products on MAM instead of the files to consumers. The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by data provider and written on the Product Contract, which ensures only data consumers can retreive it from Product Contract.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.5in]{key_exchange}
    \caption{Encryption key exchangement process.}
    \label{fig:key_exchange}
\end{figure}

>>>>

\begin{abstract} 
%cite IoT data subscription economy
The Internet of Things (IoT) makes our lives simple and easier by automating mundane processes with devices around us. Within IoT scenarios, machine-to-machine (M2M) is an inevitable technology that allows machines to own their digital assets and start participating in an economy, which devices can share and trade their resources. The real-time data exchange among devices are periodically that only data in a specific time period is interested. Thus, publish/subscribe (pub/sub) communication model of streaming data with efficiency and flexibility corresponds such use case. Additionally, the economic layer built on top of subscription-based pricing models as Software-as-a-Service (SaaS) enables monetizing the subscription relationship, which the payment of data streams is calculated with data usage instead of a particular price for a fixed data set. This pricing model allows data providers to have a better vision of managing budgets and data consumers to have the flexibility to subscribe and unsubscribe. However, unlike static data sets, the streaming data increases the importance and difficulties of dynamic data ownership and identity verification. Using certificate authorities (CAs) in such diverse nature for identity verification exposes vulnerabilities of central services, which eventually threaten the trust foundation of the entire system. Therefore, a trustless data trading infrastructure is required where the entities can trade, validate data ownership and data integrity without trusting any service or participants. Besides, consider handling the jobs and trading processes at the same time is too heavy for low-level IoT devices, an automated subscription procedures is also required. In this paper, we leverage usages of distributed ledger technologies (DLTs) to construct a decentralized and trusted data trading platform on top of the IoT brokered infrastructure. This approach can efficiently enhance the degree of transparency and scalability. The storage via an end-to-end encrypted message streams allows transmitting, accessing and validating data streams over distributed ledgers without authorities, and the trading process is automated through smart contracts. Finally, the prototype is implemented and evaluated.
\end{abstract}

\begin{IEEEkeywords}
Data Marketplace, decentralization, Distributed Ledger Technology
\end{IEEEkeywords}

@@

% SaaS
The economic incentive model in our proposed IoT data trading platform works as subscription service that valuates the payments by data usage. The subscription-based models (e.g. SaaS and platform-as-a-service (PaaS)) are embedded in our lives, such as newspaper, video/audio streaming and softwares, which can bring enormous operating incomes and offer advantages that allows service providers have the flexibility in resource planning as well as a better prediction of revenue streams. And for service consumers, they can subscribe and unsubscribe the services at will at anytime. The subscription-based model can easily adapts the underlying pub/sub communication model and benefit both data providers and consumers which promotes a good circulation of the platform. In \cite{SaaS}, the author pointed out that the strength of the relationships between consumers and providers of subscription-based services depends on the service quality (i.e., the data quality in data trading platform), and trust is key to successful subscription-based services.

%trustless & automated
%trust: 對系統、對身份、對資料
In data trading platforms, there are three major aspects that need trust: identity, data ownership and trading. Proving the identity as well as the ownership of data is a challenging issue among various roles in a large scale platform. In current systems, trusted third-party authority like CA is widely adopted to certify each member. However, building trust upon CA is dangerous and fragile. The compromise of routers or CA can break the trust of entire system, and the data portability of using third-party services is still under suspicion. Meanwhile, these concerns are taking into data storage as well, keeping data assets in a centralized data storage or cloud service meet the constraints of data portability, which may violate General Data Protection Regulation (GDPR)\cite{GDPR}. Besides CA and storage, the subscription history of data consumer may reveal his/hers interests and the exposure of personal information during trading process against GDPR as well. The final trust is trading procedures, apart from setting up the agreement between providers and consumers, both of them need to confirm that the agreement will be executed even if one party fails to comply.

@@

\subsection{Contributions}
The contributions in the paper are summarized as follow:
\begin{itemize}
	\item Standing on our proposed decentralized data trading infrastructure, we review several decentralized data trading architectures as well as the existing distributed storage, and clarify the necessity of using MAM.  
    \item We make an in-depth analysis of each layer of MAM, in addition to the performance evaluation and optimization of the current implementation. We also compare the performance of exchanging different cryptosystems.
	\item We analyze the security concerns when offloading MAM operations to brokers, and propose a solution to resolve them.
\end{itemize}

@@

%TODO: cite IOTAIndustryMarketplace
\section{Related Work}
\label{section:relatedWork}
% pub/sub
\subsection{Data exchange mechanism for IoT}
The publish/subscribe service model consists of publishers, subscribers and brokers, which has been proven\cite{pubSubAnalysis, pubSubAnalysis2} to be an efficient and flexible solution for a large number of diverse entities like IoT applications. A lot of work in publish/subscribe system focused on the scalability and the different security issues such as, encrypted data communication, privacy preserving data subscription and access control of digital asset. A few work targets on the storage which is a vital consideration for IoT and mobile computing and the incentive for data economics.

M. B. Abdullahi and G. Wang\cite{centralPubSub} presented a secure publish/subscribe data storage service in Wireless sensor networks (WSNs) which ensures several security issues. Each user has an identity for authentication, whereas subscribers' interests are encoded before matching to protect users' interests. Additionally, the proposed encryption scheme can prevent adversary to access published data if the sensor node is compromised. However, the access control and encryption keys of data is enforced by the network controllers (NCs) and CAs, which may be a potential security risk of the system. Also the storage is not well illustrated in the work. G. S. Ramachandran et al.\cite{trinity} pointed out the security risk of centralized brokers, and applied DLTs to build a distributed pub/sub system which promotes the transparency of interactions of participants and the status of data. With the help of Ethereum smart contract, users can perform data validation easily, and brokers can keep track of data status. But data is plaintext on blockchain, which the privacy problem of sensitive data need to be considered carefully. The economics incentives that can encourage the publishers to participate the system and pay more attention on the quality control are not included.

In \cite{userCentricData}, the publisher runs a node in blockchain that preserves all the history data of the ledger, therefore, they can publish and manage data without any third-parties. The subscribers request publisher directly and ask them to save a cache space for interested data. The main contribution of the system is to ensure data owners have full controls of produced data, but the data owners need to have well devices and environment to perform such functionalities and preserve data. Also, the rights for accessing digital assets is more compatible in the IoT scenarios instead of copying raw data. Secure Pub-Sub model\cite{SPS}, a brokerless of publish/subscribe model, is proposed to eliminate the security risk of middleware in the model and to provide a reputation-based fairness payment strategy on blockchain. The privacy and data security are considered thoroughly with the encryption scheme, while the reputation of publishers, payment and data sharing are deployed on smart contracts that allows all operations are transparent. The reputation system and the punishment rules against malicious acts of subscribers and publishers. Yet, without brokers, providers and subscribers may need to reveal more sensitive information like IP address in order to match the both sides. Another broker-less model in \cite{PrivacyPreservPubSub} protects the subscribers' privacy by encrypting users' interests with the light-weight PKEwET\cite{PKEwET}, which allows publishers to match the subscribers' interests in cipher text.

\subsection{Trusted IoT Trading Infrastructure}
Multiple infrastructures for trusted IoT data trading have been proposed by Paolo Missier et. al\cite{MindMyValue} presenting an IoT brokered infrastructure based marketplace which enables trading with Ethereum smart contracts. The brokers are only responsible for data transmission in order to adapt flexible agreement between participants. Unlike the standard pub/sub model that matches publishers and subscribers that participants are unaware of each other. However, the data cubes (i.e., a tuple of information, such as provider, subscriber and time period) are stored in a centralized Cassandra NoSQL database, which is guaranteed to be tamper-proof but the risk of single point failure still exists.

A. Colman et al. \cite{TrustedMarketplaceWearable} discussed on trading the sensitive data among wearables. Several security issues are well discussed and solved with DLTs in the paper, the system consists of multiple components that has its different responsibilities, such as data anonymizer eliminates keen information for privacy protection, access controller handles the key management and contract manager manages Ethereum smart contracts. While the trading processes are split into multiple servers, and the request/response communication model is applied, the scalability problem of the marketplace remains.

In the following researches, Masked Authenticated Messaging (MAM)\cite{MAM} is regarded as a secure data transmission layer and data storage built on top of DLT which provides access control, tamper-proof and authentication functionalities by tailoring messages to a channel. Jinzhi Lu et al.\cite{luDecentralizedDM} builds the data exchange system with MAM and IPFS\cite{IPFS}, a content-based addressing distributed storage system. Considering the limited transaction processing capability of DLT, the authors suggest to adopt IPFS to handle the encrypted large data sets, then add the encrypted IPFS link to MAM for further exchange. This research takes MAM as data transmission layer only that focuses on secure data exchanging architecture design and security analysis, but the trading strategies are not studied yet. A similar infrastructure proposed by Zichichi et al.\cite{SocialGood} offered a key and entry points management with MAM that minimize the information which data producers need to hold. Also, Ethereum smart contract is used to maintain an authorized user list and to enable trading. However, the access control is examined by Authentication Service, the only client/server communication architecture, where the security issues and bottleneck of system emerges from, and the details of trading and interactions between providers and consumers are not illustrated in this paper.

@@

O. Lamtzidis and J. Gialelis \cite{IOTASensorNode} proposed a distributed sensor node system to exchange data and establish a data monetization economy paradigm. The Back-End server helps sensor nodes to accelerate data uploads to MAM, manages keys and metadata of data streams, and evaluates data price according to its quality. Furthermore, the Back-End server operates an user friendly interface of the marketplace and tackles all trading procedures. The heavy loading of Back-End server encounters the system scalability problem, single point failure as well as malicious attacks which may damage the profits of all players. And the pricing strategy allows buyout, but does not take subscribe/unsubscribe based diagram into consideration. The decentralized data marketplace in \cite{DDMSmartCities} is fully decentralized without the existence of any intermediate server but data providers only, data providers attach and trade data streams via MAM. With MAM, the data streams subscription is enabled, yet the conditions and details like refund and unsubscription are not discussed in this paper.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.5in]{pub_sub_model}
    \caption{The players in data subscription-based trading platform consists of data providers, data consumers and brokers.}
    \label{fig:pub_sub_model}
\end{figure}

\begin{itemize}
\item \textbf{Data Provider: }
Data providers are the ones that generate streaming data and set the data price based on the different types of data. With the subscription fee that earned via trading, data providers are incentivized to maintain and improve the quality of data.
\item \textbf{Data Consumer: }
Data consumers are entities that are willing to buy data streams. As it is laborious to widely deploy devices to collect data from scratch, and without a marketplace, it is also difficult to find providers of the data sets, purchases is the fastest and efficient way to get the desired data sets.
\item \textbf{Broker: }
Brokers are responsible for building an agreement between data providers and consumers. Also brokers can represent data providers to perform computing tasks as brokers are expected to have higher resource.
\end{itemize}

@@

\subsection{Choice of Data Storage}
Data storage is the trust basis of data trading platforms where the data assets are reserved. Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots. Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well. In our proposed architecture, we adopt MAM as data storage to resolve the challenges of managing and verifying data streams. MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams. Carrying these properties, MAM is also appropriate for building a self-sovereign identity system where the identity information such as public key, unique identifiers of services and metadata are stored. One can easily prove himself by sharing the identifier on MAM without any authority.

@@

\begin{itemize}
    \item \textbf{Scalability}: For both data providers and consumers, MAM keeps the number of managed keys and data entry points as small as possible
    \item \textbf{Integrity}: 
	\begin{itemize}    	
        \item Messages published to the Tangle are tamper-proof that against malicious modification.
    	\item Messages are signed with the keys pre-generated under Merkle signature scheme\cite{MSS} (MSS) that both keys and messages can be verified by participants.
    \end{itemize}
    \item \textbf{Confidentiality}:
    \begin{itemize}    	
    	\item The encrypted data are uploaded that only participants that have keys can decrypt.
    	\item The authorized users can retrieve data streams, since data is written on the Tangle which can be queried as long as the IOTA network is alive.
    	\item MAM provides forward-secrecy. The entry points of future data can be derived, but it's impossible to trace back those in the past. This feature prevents adversaries from retrieving published history even if the key is revealed.
    \end{itemize}
\end{itemize}

@@

% alternative solution => IPFS(data) + MAM(index)
\subsection{Digital Identity}
The digital identity represents an entity and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions. In our architecture, a self-sovereign identity system TangleID\cite{TangleID} is used to manage the identity information that allow entities to prove its identity without any third-party authority. TangleID is built on top of MAM where change logs of the Decentralized Identifiers (DIDs)\cite{DID} defined by W3C is traceable. The identity information such as public key, unique identifiers of services and metadata consists a DID document. One can easily prove himself by sharing the identifier on MAM without any authority.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=3.5in]{TangleID}
    \caption{To participate the data trading, players are required to have DID document issued by TangleID. The Consumer first need to send a registration request to TangleID to get the MAM channel ID of DID document and a public/private key pair for authentication. When the trade establish, the consumer sends the DID MAM channel ID to provider in order to perform encryption key exchange. The data provider can then retrieve the consumer's public key and encrypt the content with it. After the consumer gets the encrypted message, he/she can decrypt the ciphertext with private key and finally get the encryption key of data product.}
    \label{fig:TangleID}
\end{figure}

@@

With the functionalities of Ethereum smart contracts, a flexible and verifiable trading mechanism can be achieved. In our system, \textbf{Product Contract} is made for the product launching and trading. The information of data products such as address of the data provider, subscription fee, brokerage fee, threshold of consent votes of refunding, MAM channel/endpoint ID (the data entry point), time period and the broker-verified encryption key are listed on Product Contract. Listing. \ref{lst:constructor} list the data fields of Product Contract, and Fig.~\ref{fig:smart_contract_mam} shows the relationship of Product Contract and MAM. Furthermore, the participants can exchange encryption keys without any authorities via smart contracts. Though this design may cost extra transaction fees than exchanging key off-chain, it is considered a more secure strategy to protect the privacy of participants.

@@

As for MAM operations, the performance results in Section.\ref{section:mam_performance} show that operating MAM costs a lot of resources for the devices, therefore we present an alternative solution for data providers to delegate these computing tasks to brokers while ensuring the privacy. The details would be further illustrated in Section.\ref{section:ta_endpoint}.

\section{Masked Authenticate Messaging}
Data storage is the trust basis of data trading platforms where the data assets are reserved. Streaming data unlike a fixed set of data which can be verified by the hash of whole pack of data, it consists of continually granular records of each time slots. Therefore, the verification such as, data integrity and source identity are narrow down to a data point as well. In our proposed architecture, we adopt Masked Authenticated Messaging (MAM)\cite{MAM} as data storage to resolve the challenges of managing and verifying data streams. MAM is the second layer data communication protocol built on top of IOTA\cite{IOTAwhitepaper} network, the Tangle, a feeless cryptocurrency designed for IoT, which introduces properties like publishing, classifying and tracking authenticated message streams. Carrying these properties, MAM is also appropriate for building a self-sovereign identity system where the identity information such as public key, unique identifiers of services and metadata are stored. One can easily prove himself by sharing the identifier on MAM without any authority.

@@

%classify
The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages. For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs. Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products. To do the classification in other distributed storage also encounters the aforementioned scalability problem, data entry points of the data steams should be reserved.

%data trace
Moreover, data traceability is an important security issue that allows users to track the changes of data. Currently, hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity. Yet the hash values of each new version are unrelated and it's hard to point out the differences between versions. MAM benefits from the singly linked-list data structure which attaches messages chronologically, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.

The operations of MAM are frequent, especially for data providers, who either upload data in a short time interval or maintain multiple MAM channels or endpoints at the same time, hence the operation of MAM is one of the potential bottleneck in data marketplace. In this paper, we evaluate the performance of MAM, and improve the efficiency with different strategies. Also, we take offloading the computation tasks to brokers as another possible approach for IoT devices, since brokers are considered to have higher computational power.

@@

\subsubsection{Plight for Low-level edge device}

\section{Decentralized Data Marketplace Case Study}
Trading Models of Decentralized Data Marketplace
\subsubsection{Set Up}
All participants need to register on TangleID\cite{TangleID}, a self-sovereign identity system built on top of MAM, enables authentication without any third party via a decentralized identifiers and a public/private key pair for authentication.

@@

The details of data product, such as data price, MAM channel/endpoint ID and time period are listed on the Product Contract. As regard to the encryption key of data product, it is certified by a broker with blind signature\cite{blindSig}, a mechanism that allows users to sign contents without knowing it, and written the signed key on the Product Contract. This provides an approach for data consumers to verify the encryption key that avoid data providers dishonest data consumers with a wrong one. The workflow is shown in Fig.~\ref{fig:launching_product}.

@@

\subsubsection{Trading}
Data consumers pay subscription fees to the Product Contract of desired data products, and data providers give the "access" of data products on MAM instead of the files to consumers. The MAM channel/endpoint encryption key is encrypted with the public key of data consumer by data provider and written on the Product Contract, which ensures only data consumers can retrieve it from Product Contract.

@@

\begin{figure}[!t]
    \centering
    \includegraphics[width=3.5in]{key_exchange}
    \caption{Encryption key exchange process.}
    \label{fig:key_exchange}
\end{figure}

\subsubsection{Refunding}
Subscribing to future data is a high-risk which data provider may not upload data as the agreement set after receiving the subscription fee. Therefore, in our proposed architecture, data consumers can initiate a refund procedure if the data is not available or defective. The subscription fee is transferred from the Product Contract to data providers when the committed data is available on MAM. When the refund procedure is launched, all consumers start voting based on their opinions on the data product. Once the ratio of consent votes of refunding is higher than a threshold, the subscription fee is proportionally transferred to the data provider, broker and every consumer.
